### 2016-06-23 filters.tex
responses to JK's comments

\heading{FP-security of hash-based filters.} \tsnote{NY give it in
the private hash setting (sort of); but, intuitively, it should be
hard to find false-positives even if you know that MD5 or SHA-x are
the hash functions.  Not totally sure how to capture this intuition
nicely.} \jnote{Not sure I agree. First of all, if $\epsilon$ is not
negligible then a random element is a false positive with noticeable
probability. Beyond that, I think that intuitively it makes sense
that if you want false positives to be hard to find then you need to
make the hash functions secret.} \tsnote{I don't think it makes sense
to talk about asymptotics or negligibility, for exactly the reason you
state. I think the key point here is: what is ``hard''?   The designer decides what FP rate is
acceptable for a given application, a given set of efficiency
constraints, the side-effects of a FP, etc.  For a fixed FP target,
she optimizes the filter size and/or the number of hash functions for
her setting. Whether the target FP rate is 0.01 or $2^{-80}$, we should be able to say (in the ROM, at least)
that it will take this-many hash computations, and this many on-line
set-membership queries, to find the first FP.  In the standard model,
with public hash functions, it is clearly more difficult to make
formal claims.  Even so, in practice I expect it would be quite expensive to
find a string~$x$ such that $(h_1(x),h_2(x),\ldots,h_k(x))$
falls in a given set of tuples when $h_i(x)=\mathrm{truncate}(\mathrm{SHA256}(\langle i \rangle
\concat x), m)$, say. (Even more so if my setting admits relatively
expensive hash computations, e.g. SCRYPT.)  BTW, your suggestion to
have a FP notion with secret~$\mathrm{S}$ is interesting here. }

@@

\jnote{How do we want to define a ``secure'' Bloom filter (even
informally)? Do we want to say that the probability of finding a
false positive is negligible? Or that if we set the FP rate to
$\epsilon$ then the best an attacker can do with $q$ hash queries is
$1-(1-\epsilon)^q$ plus negligible?} 
\tsnote{Formally, I don't think we can (and still be rooted in
  reality.)  Even informally it's hard, since the fact is that the
  designer decides what is ``secure'' for her setting.  I think we
  just say something like ``A bloom filter is
  $(t,q_h,q_m,\epsilon)$-secure if no attacker running in time at
  most~$t$, asking at most~$q_h$ hash queries and $q_m$ set-membership
  queries, has probability more than~$\epsilon$ of finding a FP.''  (If
you like, we can throw a paramter~$n$ in there, for the number of FPs
it must find.)  Perhaps informally we say that a bloom filter is
secure if, for ``reasonable'' $t,q_h,q_m$, the value of~$\epsilon$ is
not ``significantly larger'' than the designer's target.}

@@

\jnote{What parameters are needed to get negligible $\epsilon$? Are
they reasonable in practice?}

@@

\heading{Security in multiple-server settings. }  \jnote{What is the
goal here? If they don't share hash functions, I'm not sure what is
gained by considering this definition.} In this section, we consider
security notions for settings in which there may be multiple
servers, each holding a filter representation of a set.  To allow
for each server to embed server-specific information into its
representation, we abstract the servers as $B_1,B_2,\ldots,B_\ell$
where each $B_i=(\Hash_i,\Rep_i,\Qry_i)$ is an $(n,k,m)$-filter.
\tsnote{Still some kinks to be ironed out though.  The current
notions sample fresh hash functions for each server.  But in (say)
the Squid setting, the same hash functions are used across all Squid
instances... maybe it suffices, for that setting, to say that the
$\Hash_i$ are all the same, and each simply returns a fixed set
of~$k$ hash functions (i.e., deterministic).} To model insider
attacks, we give the adversary the ability to corrupt (adaptively)
instances of the filter.  Such attacks capture P2P settings, in
which the adversary may join the network as a peer.

>>>>

\heading{FP-security of hash-based filters.} \tsnote{NY give it in
the private hash setting (sort of); but, intuitively, it should be
hard to find false-positives even if you know that MD5 or SHA-x are
the hash functions.  Not totally sure how to capture this intuition
nicely.} \jnote{Not sure I agree. First of all, if $\epsilon$ is not
negligible then a random element is a false positive with noticeable
probability. Beyond that, I think that intuitively it makes sense
that if you want false positives to be hard to find then you need to
make the hash functions secret.} \tsnote{I don't think it makes sense
to talk about asymptotics or negligibility, for exactly the reason you
state. I think the key point here is: what is ``hard''?   The designer decides what FP rate is
acceptable for a given application, a given set of efficiency
constraints, the side-effects of a FP, etc.  For a fixed FP target,
she optimizes the filter size and/or the number of hash functions for
her setting. Whether the target FP rate is 0.01 or $2^{-80}$, we should be able to say (in the ROM, at least)
that it will take this-many hash computations, and this many on-line
set-membership queries, to find the first FP.  In the standard model,
with public hash functions, it is clearly more difficult to make
formal claims.  Even so, in practice I expect it would be quite expensive to
find a string~$x$ such that $(h_1(x),h_2(x),\ldots,h_k(x))$
falls in a given set of tuples when $h_i(x)=\mathrm{truncate}(\mathrm{SHA256}(\langle i \rangle
\concat x), m)$, say. (Even more so if my setting admits relatively
expensive hash computations, e.g. SCRYPT.)  BTW, your suggestion to
have a FP notion with secret~$\mathcal{S}$ is interesting here. }

@@

\jnote{How do we want to define a ``secure'' Bloom filter (even
informally)? Do we want to say that the probability of finding a
false positive is negligible? Or that if we set the FP rate to
$\epsilon$ then the best an attacker can do with $q$ hash queries is
$1-(1-\epsilon)^q$ plus negligible?} 
\tsnote{Formally, I don't think we can (and still be rooted in
  reality.)  Even informally it's hard, since the fact is that the
  designer decides what is ``secure'' for her setting.  I think we
  just say something like ``A bloom filter is
  $(t,q_h,q_m,\epsilon)$-secure if no attacker running in time at
  most~$t$, asking at most~$q_h$ hash queries and $q_m$ set-membership
  queries, has probability more than~$\epsilon$ of finding a FP.''  (If
you like, we can throw a paramter~$n$ in there, for the number of FPs
it must find.)  Perhaps informally we say that a bloom filter is
secure if, for ``reasonable'' $t,q_h,q_m$, the value of~$\epsilon$ is
not ``significantly larger'' than the designer's target.  I guess
that's not far off from one of your suggestions.}

@@

\jnote{What parameters are needed to get negligible $\epsilon$? Are
they reasonable in practice?} \tsnote{Again, I don't think that
negligible is reasonable in practice :P}

@@

\heading{Security in multiple-server settings. }  \jnote{What is the
goal here? If they don't share hash functions, I'm not sure what is
gained by considering this definition.} \tsnote{Perhaps not the same
hash functions, but correlated ones.  For example, server~$j$ uses
hash functions $\tilde{h}_i(x) = h_i(\langle \mathrm{id}_j \rangle \concat x)$ for
some $h_i$ shared among servers.  The $\mathrm{id}_j$ may or may not
be public, e.g. in a P2P network your ID might be a nonce learned only
when you join.  Also, the sets $\mathcal{S_j}$ stored at each server
might be correlated.} In this section, we consider
security notions for settings in which there may be multiple
servers, each holding a filter representation of a set.  To allow
for each server to embed server-specific information into its
representation, we abstract the servers as $B_1,B_2,\ldots,B_\ell$
where each $B_i=(\Hash_i,\Rep_i,\Qry_i)$ is an $(n,k,m)$-filter.
\tsnote{Still some kinks to be ironed out though.  The current
notions sample fresh hash functions for each server.  But in (say)
the Squid setting, the same hash functions are used across all Squid
instances... maybe it suffices, for that setting, to say that the
$\Hash_i$ are all the same, and each simply returns a fixed set
of~$k$ hash functions (i.e., deterministic).} To model insider
attacks, we give the adversary the ability to corrupt (adaptively)
instances of the filter.  Such attacks capture P2P settings, in
which the adversary may join the network as a peer.
